\PassOptionsToPackage{table,xcdraw}{xcolor}

\documentclass[sigconf,review,anonymous]{acmart}
%\acmConference[ESEC/FSE 2021]{The 29th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{23 - 27 August, 2021}{Athens, Greece}

\acmConference[ICSE 2022]{The 44th International Conference on Software Engineering}{May 21–29, 2022}{Pittsburgh, PA, USA}

%\documentclass[sigconf,review, anonymous]{acmart}
%\documentclass[sigconf]{acmart}

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{array}
\usepackage{amsmath,amsfonts}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float} 
\usepackage{listings}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\usepackage{balance}

\usepackage[skins]{tcolorbox}

\usepackage{xcolor,pifont}
\newcommand*\colourcheck[1]{%
	\expandafter\newcommand\csname #1check\endcsname{\textcolor{#1}{\ding{52}}}%
}
\colourcheck{blue}
\colourcheck{green}
\colourcheck{red}

\newtcolorbox{myframe}[2][]{%
  enhanced,colback=white,colframe=black,coltitle=black,
  sharp corners,
  toprule=1.0pt,
  rightrule=0.3pt,
  leftrule=0pt,
  bottomrule=0pt,
  fonttitle=\itshape\scshape\large,
  left=0pt,right=5pt,top=5pt,bottom=3pt,
  attach boxed title to top right={yshift=-0.3\baselineskip-0.4pt,xshift=-5mm},
  boxed title style={tile,size=minimal,left=0.2mm,right=0.5mm,
    colback=white,before upper=\strut},
  title=#2,#1
}

%\newcommand{\code}[1]{{\footnotesize\textsf{#1}}}

\newcommand{\tool}{\textsc{FixLocator}\xspace}

\newtheorem{Definition}{Definition}
\newtheorem{Claim}{Claim}
\newtheorem{Lemma}{Lemma}
\newtheorem{Theorem}{Theorem}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newtheorem{observation}{Observation}
\newtheorem{property}{Property}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\usepackage{amsthm}
 \definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}



\begin{document}

%\title[{\tool}: Deep Fault Localization with Code Coverage Representation Learning]{{\tool}: Deep Fault Localization with Code Coverage Representation Learning}

\title[{\tool}: Fault Localization to Detect Fixing Locations]{{\tool}: Fault Localization to Detect Fixing Locations}


%%%---- AUTHORS BLOCK ------

%Yi Li:New Jersey Institute of Technology;Shaohua Wang:New Jersey
%Institute of Technology;Tien Nguyen:University of Texas at Dallas 

%\author{Yi Li}
%\affiliation{
%\institution{New Jersey Inst. of Technology, USA}
%}
%\email{yl622@njit.edu}
%\author{Shaohua Wang}
%\affiliation{
%\institution{New Jersey Inst. of Technology, USA}
%}
%\email{davidsw@njit.edu}
%\author{Tien N. Nguyen}
%\affiliation{
%\institution{University of Texas at Dallas, USA}
%}
%\email{tien.n.nguyen@utdallas.edu}


%\renewcommand{\shortauthors}{Li, Wang, and Nguyen}

\setcopyright{none}

\settopmatter{printacmref=false, printfolios=false}

\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column


%(1) present information sorted in a way that a CNN can "see" patterns
%discriminating between faulty and non faulty statements more easily;

%(2) identify the actual crash statement to the network;

%(3) present more information to the deep neural network in the form of
%a summary of data dependences for each statement as well as source
%embedding; and

%(4) the suspiciousness of a statement is seen taking into account
%relationships to other statement, as opposed to a statement by itself”



%\input{sections/abstract}
\begin{abstract}
We present {\tool}, a DL-based fault localization (FL) approach
supporting the detection of buggy statements in one or multiple
methods that need to be modified accordingly in the same fix. We treat
this FL as a dual learning task with two models. First, the
method-level pairing model, \code{MethFL}, learns the methods to be
fixed together. Second, the statement-level pairing
model, \code{StmtFL}, learns the statements to be co-fixed. Learning
for a model can benefit for the other and vice versa. Exploring this
duality provides useful constraints for {\tool} to learn derive
co-fixing statements. Thus, we joinly train them simultaneously with
soft-sharing the parameters of this dual models to exploit this
duality. In addition to the new dual learning model solution, we also
explore a novel feature, which is the co-change information among
statements. We use Graph-based Convolution Network to integrate
different types of program dependencies among the statements. Our
empirical evaluation on real-world datasets shows that {\tool}
relatively improves over the state-of-the-art statement-level FL
baselines from {\bf XXX\% to XXX\%}, and reduces the statements to be
examined {\bf XXX\%},
\end{abstract}


%\settopmatter{printacmref=true, printccs=true, printfolios=false}

%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10011007.10011006.10011073</concept_id>
%<concept_desc>Software and its engineering~Software maintenance tools</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Software and its engineering~Software maintenance tools}

%\keywords{Deep Learning; Automated Program Repair; Context-based Code Transformation Learning}


\maketitle

\input{sections/intro}
\input{sections/example}
\input{sections/key-ideas}
\input{sections/overview}
\input{sections/approach_step1}
\input{sections/approach}
%\section*{Acknowledgments}
%This work was supported in part by the US National Science Foundation
%(NSF) grants CCF-1723215, CCF-1723432, TWC-1723198, CCF-1518897, and
%CNS-1513263.

\newpage

\balance

%\bibliographystyle{plain}
%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{ACM-Reference-Format}

\bibliography{References}

\end{document}
