\subsubsection{\bf {\em Dataset}}


We use a benchmark dataset Defects4J V2.0.0 \cite{defects4j} with 835
bugs from 17 Java projects. For each bug in a project $P$, Defects4J
has the faulty and fixed versions of the project. The faulty and fixed
versions contain the corresponding test suite relevant to the
bug. With the \code{Diff} comparison between faulty and fixed versions
of a project, we can identify the faulty statements. Specifically, for
a bug in $P$, Defects4J has a separate copy of $P$ but with only the
corresponding test suite revealing the bug. For example, $P_1$, a
version of $P$, passes a test suite $T_1$. Later, a bug $B_1$ in $P_1$
is identified. After debugging, $P_1$ has an evolved test suite $T_2$
detecting the bug. In this case, Defects4J has a separate copy of the
buggy $P_1$ with a single bug, together with the test suite
$T_2$. Similarly, for bug $B_2$, Defects4J has a copy of $P_2$
together with $T_3$ (evolving from $T_2$), and so on. We do not use
the whole T of all test suites for training/testing. For
within-project setting, we test one bug $B_i$ with test suite
$T_{(i+1)}$ by training on all other bugs in $P$. We conducted all the
experiments on a server with 16 core CPU and a single Nvidia A100 GPU.

In Defects4J-v2.0, regarding the statistics on the number of
buggy/fixed statements for a bug, there are 199 bugs with one
buggy/fixed statement, 142 bugs with two, 90 bugs with three, 78 bugs
with four, 43 bugs with five, and 283 bugs with $>$5 buggy
statements. Regarding the statistics on the number of buggy/fixed
methods/hunks for a bug,
%bugs with multiple buggy methods/hunks,
there are 199 bugs with one-method/one-statement, 105 bugs with
one-method/multi-statements, 142 bugs with multi-methods/one-statement
for each method, 61 bugs with multi-methods/multi-statements for each
method, and 357 bugs with multiple methods, each has one or multiple
buggy statements. Thus, there are {\em 665 (out of 864 bugs) with CC
fixing statements}.




%Type 1: 199
%Type 2: 105
%Type 3: 142
%Type 4: 61
%Type 5: 357
%co-change (type 2-5): 665

%	{\em \bf Type-1. One-Hunk, One-Statement}: A bug with the fix involving only one hunk with one statement.
	
%	{\em \bf Type-2. One-Hunk, Multi-Statements}: A bug with the fix involving only one hunk with multiple statements.
	
%	{\em \bf Type-3. Multi-Hunks, One-Statement}: A bug with the fix involving multiple hunks; each hunk with one fixed statement.
	
%	{\em \bf Type-4. Multi-Hunks, Multi-Statements}: A bug with the fix involving multi-hunks; each hunk with multiple statements.
	
%	{\em \bf Type-5. Multi-Hunks, Mix-Statements}: A bug with the fix involving multiple hunks, and some hunks have one statement and other hunks have multiple statements.

\iffalse

\begin{table}[t]
	\caption{Defects4J Dataset}
	\begin{center}
		\renewcommand{\arraystretch}{1}
		\begin{tabular}{p{2.2cm}|p{3.3cm}|p{1.5cm}}
			\hline
			Identifier &  Project Name & \# of Bugs\\
			\hline
			Chart & jfreechart & 26\\
			Cli & 	commons-cli & 39\\
			Closure & closure-compiler	 & 174\\
			Codec & commons-codec & 18\\
			Collections & commons-collections & 4\\
			Compress & commons-compress	 & 47\\
			Csv & 	commons-csv & 16\\
			Gson & gson & 18\\
			JacksonCore & jackson-core & 26\\
			JacksonDatabind & jackson-databind	 & 112\\
			JacksonXml & 	jackson-dataformat-xml & 6\\
			Jsoup	 & jsoup & 93\\
			JxPath & commons-jxpath & 22\\
			Lang & 	commons-lang & 64\\
			Math & 	commons-math & 106\\
			Mockito	 & mockito & 38\\
			Time & joda-time & 26\\			
			\hline
		\end{tabular}
		\label{dataset}
	\end{center}
\end{table}

\fi
