\subsubsection{\bf RQ3. Sensitivity Analysis Results.}\label{sensi}

\begin{table}[t]
	\caption{RQ3. Sensitivity Analysis of Method- and Statement-Level Features. ML: Method-level; SL: Statement-level.}
        \vspace{-6pt}
	{\footnotesize
		\begin{center}
			\renewcommand{\arraystretch}{1}
			\begin{tabular}{p{0.3cm}<{\centering}|p{3cm}|p{0.3cm}<{\centering}|p{0.3cm}<{\centering}|p{0.2cm}<{\centering}|p{0.2cm}<{\centering}|p{0.15cm}<{\centering}|p{0.15cm}<{\centering}|p{0.5cm}<{\centering}}
				\hline
				\multicolumn{2}{c|}{\multirow{2}{*}{Model Variant}}    & \multicolumn{6}{c|}{Hit-n@Set}& \multirow{2}{*}{EXAM}\\
				\cline{3-8}
				                 \multicolumn{2}{c|}{}   &1&2&3&4&5&5+&\\
				
				\hline 
				\multirow{4}{*}{ML}&w/o Method Content              & 366 & 158 & 78  & 39 & 9 & 3   & 0.08\\\cline{2-9}
				&w/o	Method Structure	                        & 357 & 155 & 80  & 40 & 8 & 3   & 0.08\\ \cline{2-9}
				&w/o Similar Buggy Method    	& 361 & 157 & 79  & 44 & 9 & 3   & 0.08\\ \cline{2-9}
				&w/o ML Co-change Relat.         & 355 & 152 & 77  & 40 & 8 &  3  &0.09 \\ \cline{2-9}
				\hline
				\multirow{4}{*}{SL}&w/o Code Coverage               & 348 & 151 & 75  & 38 & 7 & 2   & 0.09\\\cline{2-9}
				&w/o	AST Subtree	        & 354 & 153 & 77  & 41 & 8 & 3   & 0.09\\ \cline{2-9}
				&w/o Variables               	& 373 & 162 & 78  & 42 & 9 & 3   & 0.08\\ \cline{2-9}
				&w/o SL Co-change Relat.        & 351 & 150 & 76 & 39 & 7 &  2  & 0.11 \\ \cline{2-9}
				%&w/o Co-change Relation          & 342 & 148 & 73  & 37 & 6 & 2   & 0.11\\
				\hline
			&	\tool                           & 387 & 167 & 82  & 46 & 9 & 3   & 0.07\\ \cline{2-9}
				\hline
			\end{tabular}
			
			\label{fig:rq3-1}
		\end{center}
	}
\end{table}

Table~\ref{fig:rq3-1} shows the ablation analysis of the impact of
different features and relations among methods/statements on
{\tool}'s performance.

\underline{Impact of method-level (ML) features and ML co-change relation.}
Among the method-level features/attributes of {\tool}, the {\it method
structure feature represented as AST has the largest impact}. Without
the method structure feature, Hit-1@Set is decreased by 7.8\% and
EXAM score is increased by 14.3\%.
%the performance is decreased by 7.8\% in terms of Hit-1@Set and
%increased the EXAM score by 14.3\%.
The method content feature has less impact than the
similar-faulty-method one. This shows that {\em the bugginess nature
of a method and similar ones has more impact than the tokens of the
method itself}.

Moreover, the ML co-change relations among methods have a larger
impact than any ML features on the performance. Specifically,
without the co-change feature among methods, Hit-1@Set is decreased
by 8.3\% and EXAM score is increased by 28.6\%.
%the performance is decreased by 8.3\% in terms of Hit-1@Set and
%increased the EXAM score by 28.6\%.
This result shows that {\em our novel feature of co-change relation is
important for detecting CC fixing locations}.

%it can decrease the results of Hit-1@Set by xx\% and increase the Exam
%score by xx\%.

\underline{Impact of statement-level (SL) features and SL co-change relation.}
Among the statement-level features, {\it Code Coverage
has the largest impact}. Without {\it Code Coverage} feature,
Hit-1@Set is decreased by 10.1\%, and EXAM score is increased by 28.6\%.
%the performance is decreased by 10.1\% in terms of Hit-1@Set and is
%increased by 28.6\% in terms of EXAM score.
The subtree feature has more impact on performance than the
variable feature.

Moreover, the co-change relations among statements also have a larger
impact than any SL features/attributes on the performance. Specifically,
without co-change relations among statements, Hit-1@Set is decreased
by 9.3\%, and EXAM score is increased by 57.1\%. Thus, {\em the novel
feature of co-change relation is also very important for detecting
CC fixing statements}.




\underline{Impact of the depth level of stack trace.} 
As seen in Table~\ref{fig:rq3-2}, the depth level of stack trace can
have a large impact on the performance. Specifically, when the depth =
10, {\tool} can achieve the best performance in all metrics. The cases
with depth = 5 or 15 can bring into analysis too few relevant methods
or too many irrelevant methods. Thus, we chose depth=10 for other
experiments.

%Thus, the results for depth=5 or 15 are lower than the ones of depth=10.

\begin{table}[t]
	\caption{RQ3. Sensitivity Analysis (Depth of Traces).}
        \vspace{-6pt}
	{\footnotesize
		\begin{center}
			\renewcommand{\arraystretch}{1}
			\begin{tabular}{p{1cm}|p{0.3cm}<{\centering}|p{0.3cm}<{\centering}|p{0.3cm}<{\centering}|p{0.3cm}<{\centering}|p{0.3cm}<{\centering}|p{0.3cm}<{\centering}|p{0.7cm}<{\centering}}
				\hline
				\multirow{2}{*}{Depth}    & \multicolumn{6}{c|}{Hit-n@Set}& \multirow{2}{*}{EXAM}\\
				\cline{2-7}
				&1&2&3&4&5&5+&\\
				
				\hline 
				5 			                & 371 & 162 & 74  & 42 & 8 & 3   & 0.09\\
			{\bf	10}                         & 387 & 167 & 82  & 46 & 9 & 3   & 0.07\\
				15	                        & 368 & 158 & 71  & 39 & 7 & 3   & 0.10\\
				\hline
			\end{tabular}
			
			\label{fig:rq3-2}
		\end{center}
	}
\end{table}


%Our results show that all features and components in {\tool} have
%impacts on its performance.
